\chapter{Conclusions and and Future Directions} \vspace{10mm}\begin{quote}  {\it ``I conclude that musical notes and rhythms were first acquired    by the male and female progenitors of mankind for the sake of    charming the opposite sex.''} --- Charles Darwin\end{quote}\vspace{7mm}\section{Automatic Music Transcription}\vspace{5mm}The most immediate application of the ideas behind {\it Riddim}is in an automatic music transcription system.  Traditionally, transcription involves writing down the notes occurring in apiece of music, converting an acoustic signal to a symbolicrepresentation \cite{Klapuri:98}. Learning to transcribe music involves however, a lifetime of musical trainingand specific training in the styles to be transcribed. Anautomatic transcription software tool thus saves time and is useful for musicians and composers for a variety of analytic and pedagogical purposes. For example, in many modern styles where a score is not available, a symbolic representation of what is occurring in the music is very valuable. Similarly, Jazz buffs trying to learn the intricacies of an improvised jazz solo can benefit from such a system as well as can academic composers trying to analyse an electro-acoustic work.To make {\it Riddim} a robust music transcription system will entail additional work. First, a fundamental frequency tracking module is essential for a classic ``score'' transcriber. This module would essentially traverse the extracted streams performing a pitch estimation at every onset point. In thisway, the onset times would correspond to the rhythmic partof the score while the estimated fundamental frequency wouldapproximate the pitch. Invariably, as audio analysis techniques become more sophisticated,automatic music transcription systems like speech recognitionsystems are going to be increasingly important in the way peoplelearn and interact with music. As Klapuri points out, ``Some peoplewould certainly appreciate a radio receiver capable of trackingjazz music simultaneously on all channels'' \cite{Klapuri:98}.\vspace{7mm}\section{{\it Riddim} in Real-time}\vspace{5mm}One of the central motivations of this thesis was to take the musicthat I have composed from the studio to the stage, without compromising the complexity. At the same time, moving to a more improvisational performance setting requires a certain mastery of the musical content and the tools to be able to compose on the fly. The current work is ofcourse non-realtime. Working with the algorithms and the code for thepast nine months, I have determined that a realtime version is notonly feasible, but with minimal additional work, can run as aMAX/MSP{\texttrademark} external DSP module or as a VST{\texttrademark} plugin.\vspace{7mm}\section{Live Improvised Performance and the Meta DJ}\vspace{5mm}Once running in real-time, what are its musical applications? In a live performance setting where listening and playing within a shared musical context is paramount, {\it Riddim} ``listens'' to the surroundingmusic, analyses it and reveals patterns that can be used time a newinstrument or part. How these patterns are mixed with the originalmaterial is a delicate question of production and aesthetics, as thechoice of voicing makes a world of difference.Furthermore, in analysing and re-interpreting music on the fly, mixingelements occurs in an abstract representation of the music rather than the common DJ practise of mixing the concrete representation of the music i.e. samples.The idea of a {\it Meta DJ} involves mixing an abstract representationof ``vinyl cuts'' or CD tracks by synchronising the realtime outputs of {\it Riddim} andrendering the patterns with variety of instruments appropriate for themusical setting. The flexibility of not having to mix concrete samplesis significant since resampling, time-stretching and vocoder artifacts are commonbyproducts trying to match two tracks at different tempi. Furthermore, the time patternsextracted in realtime can be used to control light shows, smokemachines or any number of patterned sensory stimuli that accompany themusic. 